\documentclass[a4paper,10pt,twoside,twocolumn]{dndbook} %a4, 10pt, book (idk why i did that...), 2 cols, dnd-themed
\usepackage[english]{babel} %language
\usepackage[utf8]{inputenc} %lovely utf-8
\usepackage{graphicx} %images
\usepackage{wrapfig} %images
\usepackage{array} %allways use this shit, idk why
\usepackage{tikz} %draw stuff
\usepackage{ifthen} %draw stuff
\usetikzlibrary{shapes,calc,fadings} %draw stuff
\usepackage{xspace} %usefull idk, allways import this stuff
\usepackage{dirtytalk} %\say because fuck it
\usepackage{setspace} %don't ask, kind of like it...
\usepackage{pgfplots}

\usepackage[singlelinecheck=false]{caption} %idk dndbook...
\usepackage{listings} %idk dndbook...
\usepackage{shortvrb} %not used yet...
\usepackage{stfloats} %idk dndbook
\usepackage{dirtytalk}

\singlespacing
\makeatletter %because of titlepage and \HUGE

\@openrightfalse %no empty pages

\graphicspath{ {./images/} }

\def \license {GNU Free Documentation License}
\def \licensetext {Please consider and respect the copyleft of this license. The content of this document should be accessible to everyone. Everyone has the right to use the content of this document as he/she wishes, to modify it, to publish it modified (taking into account the copyleft) and to republish it without any changes (taking into account the copyleft).}
\def \author {Sven Hugi}%if you edit this document, add your name... <3
\def \illustrators {} %add name
\def \othercontrib {} %add name

%highlighting with some random effect -> looks handmade and i love it...
\newcommand\hl[2][yellow]{
	\begin{tikzpicture}[
	baseline,
	decoration={random steps,amplitude=1pt,segment length=15pt},
	outer sep=-15pt, inner sep = 0pt
	]
	\node[decorate,rectangle,fill=#1,anchor=text]{#2\xspace};
	\end{tikzpicture}
}
%2 column layout hack...
\newcommand{\nextPage}{
	\newpage
	\hbox{}
	\newpage
}
%make bad things look ok...
\newcommand{\doublelinebreak}{
	\linebreak\linebreak
}
%the old HUGE fontsize
\newcommand\HUGE{\@setfontsize\Huge{60}{80}} 

\renewcommand{\maketitle}{
	\thispagestyle{empty}
	\onecolumn %fuck it
	\vspace*{5cm}
	\begin{center}
		$\vspace*{2cm}$
			{\HUGE\DndFontDropCap{SHADAR KAI}}\\	
	\end{center}
	\twocolumn %reset shit
}\makeatother

\begin{document}
	\maketitle
	\section*{Credits}
	\vspace{.25cm}
	\textbf{Authors:} \author\linebreak
	\textbf{Illustrators:} \illustrators\linebreak
	\textbf{Additional Contributors:} \othercontrib\linebreak
	\textbf{License:} \license\doublelinebreak
	\licensetext\doublelinebreak
	\vfill\pagebreak\hbox{}\vfill\hfill{\tiny This Document was written in \LaTeX.}\pagebreak\vfill\pagebreak
	\section{Shadar-Kai Traits}
	\textbf{Ability Score Increase.} Your Dexterity score increases by 2 and your Charisma score increases by 1.\linebreak
	\textbf{Age.} Shadar-Kai have a incredibly long lifespan. But they get eaten by the Shadow Curse. They do not fear death and mostly die young.\linebreak
	\textbf{Alignment.} They thend towards Neutral\linebreak
	\textbf{Size.} Shadar-Kai stand around 6 feet tall and average about 150 pounds. Your size is Medium.\linebreak
	\textbf{Speed.} Your base walking speed is 30ft.\linebreak
	\textbf{Language.} You can read, write and speak Common and Elven or Sylvan. If you want to you can also add the dead language Netherese\linebreak
	\textbf{Darkvision.} You can see in dim light within 60 feet of you as if it were bright light, and in darkness as if it were dim light. You can't discern color in darkness, only shades of gray.\linebreak
	\textbf{Shadar-Kai Weapon Training} You have proficiency with the Spiked Chain, a special weapon.\linebreak
	\textbf{Fey Ancestry.} You have advantage on saving throws against being charmed, and magic can't put you to sleep.\linebreak
	\textbf{Unseen.} You are proficient in the Stealth skill.\linebreak
	\textbf{Eyes of Shadow.} You have advantage on Saves against detecting illusions (Magic) and if you or a other friendly Shadar-Kai casts the Darkness Spell you can see through. Also a creature can not get advantage on Stealth checks against you by hiding only in darkness.
	\textbf{Shadow Curse.} Any time you get stunned, petrified, paralyzed or unconscious (expect if it's because of willingly sleeping) you need to succeed on a DC 15 Will save or a part of your soul gets dragged to the Plane of Shadow. If the soul is fully eaten by the Planes of Shadow (note hp for your soul or better ask your dm) you transform to a wraith (and die). You can use a gal-ralan to keep your soul and body connected. You can not be raised from the dead or resurrected while you suffer from this curse. While on the Plane of Shadow the curse has no effect and can be cured with a greater restoration spell. On the Material Plane only a wish or miracle spell can end the curse. A remove curse spell does nothing against this curse.\linebreak
	To avoid being affected by the curse, most Shadar-Kai live extreme lifestyles, embracing strong emotions and peak experiences. Most of them use pain to keep their focus, decorating their bodies with tattoos, scarification and piercings in extremely sensitive parts of their bodies. Likewise, some of them engage in self-flagellation, to the point of self-harm if they fell that they getting overtaken by the curse.
	
	
	\begin{DndSidebar}{Spiked Chain}
		\begin{DndTable}{llX}
			Slashing & 2d4 & Finesse, Light, Two-Handed, Special, Ranged (10$^{ft}$)
		\end{DndTable}
		\textbf{Special} You can use you Attack to hit every creature in a 10ft radius and deal 1d4 Slashing Damage.\linebreak
		\textbf{Special} After using your Attack you can use your Bonus Action to Attack a second time and do 1d4 Slashing Damage on one Creature. If your previous Attack not hit, you can instead deal 2d4 Slashing Damage.
	\end{DndSidebar}
	
	
\end{document}